Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-14 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued II} Updating...

Since we cannot restrict our convex interval-valued function mapping
only finite number of intervals, let's consider another natural interval-valued
function. Before we consider them, we review the counterpart of Wright-convex,
Wright-concave\nb\cite{Brzdek_2014}.

\begin{definition}A function\nb$c:\left[0,1\right]\rightarrow\left[0,1\right]$
is called Wright-concave if for any three numbers\nb$x_{0}$, $x_{1}$,
and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies $c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)$.\end{definition}

\begin{example}Given a concave function\nb$c:$ For any $\delta\ge0$,
there is an additive interval-valued function\nb$\iota_{\delta}':\left[0,1\right]\rightarrow\mathscr{I}_{\delta}'$
defined by\end{example}

>>>>

Since we cannot restrict our convex interval-valued function mapping
to only finite number of intervals, let's consider another family
of natural interval-valued functions.

\begin{lemma}Given a function\nb$c:\left[0,1\right]\rightarrow\left[0,1\right]$
satisfying the following conditions:
\begin{itemize}
\item For all $x\in\left[0,1\right]$, $c\left(x\right)\le x$.
\item For all $x\in\left[0,1\right]$, $c\left(1-x\right)=c\left(x\right)$.
\item $c$ is Wright-concave\nb\cite{Brzdek_2014}, i.e., for any three
numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies $c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)$.
\end{itemize}
Then, there is a convex interval-valued function\nb$\iota_{c}':\left[0,1\right]\rightarrow\mathscr{I}_{c}'$
defined by $\iota_{c}'\left(x\right)=\left[x-c\left(x\right),x+c\left(x\right)\right]$,
where $\mathscr{I}_{c}'=\set{\iota_{c}'\left(x\right)}{x\in\left[0,1\right]}$.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $c\left(x\right)\le x$, $0\le x-c\left(x\right)$. Also, $c\left(x\right)=c\left(1-x\right)\le1-x$
implies $x+c\left(x\right)\le1$. Therefore, $\iota_{c}'\left(x\right)=\left[x-c\left(x\right),x+c\left(x\right)\right]\subseteq\left[0,1\right]$.
\item For any $x\in\left[0,1\right]$, $\iota_{c}'\left(1-x\right)=\left[1,1\right]-\left[x-c\left(1-x\right),x+c\left(1-x\right)\right]=\left[1,1\right]-\iota_{c}'\left(x\right)$.
\item Since $c\left(0\right)\in\left[0,1\right]$ and $c\left(0\right)\le0$,
we have $c\left(0\right)=0$. Therefore, $\iota_{c}'\left(0\right)=\left[0,0\right]$,
and $\iota_{c}'\left(1\right)=\left[1,1\right]-\iota_{c}'\left(0\right)=\left[1,1\right]$. 
\item Given any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have
\begin{equation}\eqalign{ 
 & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
\Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
 & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\textrm{ .} }\end{equation}
Also, 
\begin{equation}\eqalign{ 
 & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
\Rightarrow & -c\left(x_{0}+x_{2}\right)-c\left(x_{1}+x_{2}\right)\le-c\left(x_{0}+x_{1}+x_{2}\right)-c\left(x_{2}\right)\\
\Rightarrow & \left[x_{0}+x_{2}-c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}-c\left(x_{1}+x_{2}\right)\right]\\
 & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\textrm{ .} 
}\end{equation}
The above two equations implies $\iota_{c}'\left(x_{0}+x_{1}+x_{2}\right)+\iota_{c}'\left(x_{2}\right)\subseteq\iota_{c}'\left(x_{0}+x_{2}\right)+\iota_{c}'\left(x_{1}+x_{2}\right)$.
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota_{c}'\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota_{c}'\left(x_{i}\right)$
by inducting on the convex condition listed previously with $x_{2}=0$.
\end{itemize}
\end{proof}
